### 2017-02-01 local-capability-machine.tex
Use the right future world relation in the malloc lemma.

\begin{lemma}[Malloc is safe to pass to adversary]
  If $W(r) = \iota$ with $\iota \futurewk \iota_{\malloc,0}$, then
  $\npair{c_\malloc} \in \stdvr(W)$ for all $n$.
\end{lemma}
\begin{proof}
  TODO
\end{proof}

>>>>

\begin{lemma}[Malloc is safe to pass to adversary]
  If $W(r) = \iota$ with $\iota \futurestr \iota_{\malloc,0}$, then
  $\npair{c_\malloc} \in \stdvr(W)$ for all $n$.
\end{lemma}
\begin{proof}
  TODO
\end{proof}
